Comparing MTurk and the US Population's Occupational Diversity

### 2018-09-21 Manuscript.Rmd
Edited ethnicity analysis to only include ethnicities which data are available from BLS.

#Get MTurk ethnicity data
MTurk_eth <- MTurk17 %>%
  count(MTurk17$With.which.ethnicity.do.you.most.identify.)

@@

#Sum chi-square values.
sum(eth_ch2$chi2, na.rm=TRUE)
```

>>>>

#Get MTurk ethnicity data
MTurk_eth <- MTurk17 %>%
  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
MTurk_eth <- MTurk_eth[c(1:4), ]

@@

#Sum chi-square values.
sum(eth_ch2$chi2, na.rm=TRUE)
```
###Education Analysis 
```{r}
#Education Analysis 
#Clean BLS Data. Get totals.  
BLS_education_original <- read_excel("education_demo.xlsx")
BLS_education <- as.data.frame(BLS_education_original[8:14, ])
BLS_education <- BLS_education[1, c(-2, -3, -6)]
names(BLS_education) <- c("category", "High school graduates, no college(1)", "Some college, no degree", "Associate degree", "Bachelor's degree only", "Advanced degree")

#Combine categories as necessary. Get proportions.  
highschool_ged <- c(as.numeric(BLS_education$`High school graduates, no college(1)`) + as.numeric(BLS_education$`Some college, no degree`))
two_year_deg <- as.numeric(BLS_education$`Associate degree`)
four_year_deg <- as.numeric(BLS_education$`Bachelor's degree only`)
advanaced_deg <- as.numeric(BLS_education$`Advanced degree`)
BLS_education <- c(highschool_ged, two_year_deg, four_year_deg, advanaced_deg)
names(BLS_education) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
BLS_total <- as.numeric(sum(BLS_education))

#Function to find proportion for each iteration of the vector. 
e_prop <- function(x) {
  e <- x/BLS_total
}

#Use vapply and the above function to get expected proportions from BLS data
BLS_edu <- sapply(BLS_education, prop_func)

#Clean MTurk Data
MTurk_education <- MTurk17 %>%
  count(MTurk17$What.level.of.education.have.you.completed.)
colnames(MTurk_education) <- c("education level", "n")
advanced_deg <- as.numeric(MTurk_education[4,2]) + as.numeric(MTurk_education[5,2])
MTurk_education <- rbind(MTurk_education, advanced_deg)
MTurk_education[6,1] <- "advanced degree"
MTurk_edu <- MTurk_education[c(-4, -5), ]

#Define confidence intervals 
eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0/95, methods = "exact")
eduCI <- eduCI[ , 4:6]

#Build Education table 
education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
View(education_table)

#Education chi squared test
edu_ch2 <- as.data.frame(chi2(education_table))
names(edu_ch2) <- c("chi2")
row.names(edu_ch2) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
edu_ch2 <- na.omit(edu_ch2)
View(edu_ch2)

#Sum chi-square values.
sum(edu_ch2$chi2, na.rm=TRUE)
```
